---
title: "BigMac"
author: "Brandon Medina"
date: "2/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 
Get an estimated demand curve for Big Mac's

```{r}
BigMdata = read.csv('BigMac.csv')
attach(BigMdata)
```

plot the data

```{r}
plot(Demand, Price)
```


Fit an linear model

```{r}
model1 = lm(Price~Demand)
priceone=4.95
summary(model1)
plot(Demand, Price)
abline(model1)
abline(h=priceone, col='red')
grid()
```


Price Elasticity is the percent change in quantity demanded divided by the percent change in price

The marginal revenue of any product is the additional revenue that I earn by selling one additional unit (big mac)

Marginal revenue is related to price elasticity by 

MR = price * (1+elasticity)/elasticity

At McDonald's MR = MC

E = slope of demand at price P * (price/quantity)

```{r}
slope = model1$coefficients[2]
intercept = model1$coefficients[1]
demanded = (priceone-intercept)/slope

E = slope * priceone/demanded

MR = priceone * abs((1+E)/E)

print(paste('Price= ',priceone))
print(paste('Demanded= ',round(demanded,2)))

print(paste('Elasticity= ' ,round(E,2)))
print(paste('MR= ', round(MR,2)))
```

Profit = price - cost = 4.5 - MC

```{r}
Profit = priceone - MR
print(paste('Profit= $',round(Profit,2)))
```

























